The \dealii Library, Version 9.5

### 2023-06-26 9.5/paper.tex
dont show internal interfaces

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on \texttt{parallel::distributed::Triangulation} objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose we introduce a free function that computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector indicating entities of a given triangulation (in the form of \texttt{GridTools::Cache}) that intersections are computed upon.
Each entity (face or cell) is described by a vector of vertices.

\begin{c++}
// compute intersections on distributed triangulation
auto intersection_data =
       GridTools::internal::distributed_compute_intersection_locations(
         cache, intersection_requests, global_bboxes, marked_vertices,
         tolerance);
\end{c++}

\todo[inline]{Marco: It is unfortunate that we advertise a function in
  namespace `internal' here. We should think about moving it, see \url{https://github.com/dealii/dealii/issues/15463}.}

The above function uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()} internally to compute intersections between two geometric entities.

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections to evaluate the underlying physical coupling terms.
The \texttt{intersection\_data} returned by the function above can convert itself to data which can be used to fill \texttt{RemotePointEvaluation}.
The whole procedure is done communication-free.
\begin{c++}
// distribute n_points_1D quadrature points to the intersections
auto point_data = intersection_data.template
       convert_to_distributed_compute_point_locations_internal<dim>(
         n_points_1D, tria, mapping,
         // The following parameter is optional and setting it to 
         // true requires additional communication
         consistent_numbering_of_sender_and_receiver);

// use point_data to reinit RemotePointEvaluation
Utilities::MPI::RemotePointEvaluation<dim> rpe;
rpe.reinit(point_data,tria, mapping);
\end{c++}

@@

The interface described above and an early version of the wrapper have
been used successfully in~\cite{heinz2023high} to perform Nitsche-type
mortaring in the context of the conservative formulation of acoustic
equations discretized with a discontinuous Galerkin method to suppress
artificial modes.

>>>>

\subsubsection{Intersected meshes}
In the current release, we added experimental support to compute intersections on \texttt{parallel::distributed::Triangulation} objects using \texttt{CGAL}~\cite{cgal-user-ref}.
For this purpose, we introduced a free function \texttt{distributed\_compute\_intersection\_locations()} that computes intersections and relevant information for communication from \texttt{intersection\_requests}.
\texttt{intersection\_requests} is a vector indicating entities of a given triangulation that intersections are computed upon.
Each entity (face or cell) is described by a vector of vertices.
Currently, the function is placed in \texttt{GridTools::internal}, but the location and arguments of the function might still change in the future.
To compute intersections between two geometric entities, the function internally uses the new function \texttt{CGALWrappers::compute\_intersection\_of\_cells()}.

For the common case of Nitsche-type mortaring, quadrature points must be distributed on the intersections to evaluate the underlying physical coupling terms.
The data structure returned by \texttt{distributed\_compute\_intersection\_locations()} can convert itself to a data structure that can be used to fill \texttt{RemotePointEvaluation}.
This conversion is triggered by the member function~\texttt{convert\_to\_distributed\_compute\_point\_locations\_internal()}, given the number of quadrature points per intersection.
The whole procedure is done communication-free.

@@

The procedure described above and an early version of the wrapper have
been used successfully in~\cite{heinz2023high} to perform Nitsche-type
mortaring in the context of the conservative formulation of acoustic
equations discretized with a discontinuous Galerkin method to suppress
artificial modes.
